\begin{bibsection}
% \item R.N.\ Slaybaugh. ``Commercialization of  Nuclear Fusion Summit" Moderator, Nuclear Fusion: Reacting To Commercialization by VLAB. Palo Alto, CA. 14 Nov.\ 2017. (invited)


\item A.S. Voyles, \enquote{\href{https://null}{Isotope Production Activities at LBNL and LANSCE-IPF: Development of a new Nb(p,x)\ce{^{90}Mo} Monitor Reaction and Fe,La(p,x) Production Cross-Section Measurements}.} \nth{17} International Workshop on Targetry and Target Chemistry, Coimbra, Portugal. 30 August 2018.


\item A.S. Voyles, \enquote{\href{https://indico.cern.ch/event/686407/contributions/2943775/}{Isotope production cross section measurements at the HFNG, LANL-IPF, and LBNL}.}  \nth{14}  Nordic Meeting on Nuclear Physics, Longyearbyen, Norway. 24 May 2018.

\item A.S. Voyles, \enquote{\href{https://github.com/avoyles/presentations/blob/master/2018-02-12-UCBNE_colloquium/Voyles_12_Feb_2018_NE_Colloquium_Talk.pdf}{Cross-Section Measurements for Novel Medical Radionuclides at UCB/LBNL: The Challenge of \enquote{Simple} Experiments}.} UC Berkeley NE Dept.\ Graduate Colloquium, Berkeley, CA. 12 February 2018. (invited)

\item A.S. Voyles, \enquote{\href{https://github.com/avoyles/presentations/blob/master/2017-05-19-oslo_summer_school/Voyles_19_May_2017_Oslo_Summer_School.pdf}{Medical Isotope Production at Berkeley}.} University of Oslo Nuclear Physics Summer School, Oslo, Norway.  19 May 2017. (invited)

\item A.S. Voyles, \enquote{\href{http://tid.uio.no/workshop2017/talks/OsloWS17_Voyles.pdf}{Spin Distribution of Excited Nuclear States in $^{\text{nat}}$Fe(p,$\alpha$n)}.} \nth{6} Workshop on Nuclear Level Density and Gamma Strength, Oslo, Norway. 08 May 2017.


\item A.S. Voyles, \enquote{\href{https://indico.bnl.gov/event/1743/contributions/3189/}{Experimental Activities in Berkeley}.} US National Nuclear Data Week  (CSEWG), Upton, NY. 14 November 2016.


\item A.S. Voyles, \enquote{\href{https://slideslive.com/38898186/64cu-and-47scnp-crosssection-measurements-for-medical-radionuclide-production}{\ce{^{64}Cu} and \ce{^{47}Sc} (n,p) Cross-Section Measurements for Medical Radionuclide Production}.} \nth{16} International Workshop on Targetry and Target Chemistry, Santa Fe, NM. 30 August 2016.

\item A.S. Voyles, \enquote{\href{https://github.com/avoyles/posters/blob/master/2016-06-07-UITI/Voyles_UITI2016_Poster_OsloUpdate.pdf}{Neutron Cross-Sections for Radionuclide Production}} (Poster).  University \& Industry Technical Interchange 2016 Review Meeting, Raleigh, NC. 07 June 2016.

\item A.S. Voyles, \enquote{GEANT4 Simulation of Irradiation Facilities and Neutron Sources at University of Utah TRIGA for
Nuclear Forensics and Detection.}  AICHE Annual Meeting, Minneapolis, MN. 19 October 2011.

\item A.S. Voyles, \enquote{GEANT4 Simulation of Irradiation Facilities and Neutron Sources at University of Utah TRIGA for
Nuclear Forensics and Detection.}  \nth{2} National Conference in Advancing Tools and Solutions for
Nuclear Material Detection, Salt Lake City, UT. 02 May 2011.

\item A.S. Voyles, \enquote{GEANT4 Simulation of Irradiation Facilities at University of Utah TRIGA (2011).} 
ANS Student Conference, Atlanta, GA. 15 April 2011.

\end{bibsection}

