\begin{bibsection}
% \item R.N.\ Slaybaugh. ``Commercialization of  Nuclear Fusion Summit" Moderator, Nuclear Fusion: Reacting To Commercialization by VLAB. Palo Alto, CA. 14 Nov.\ 2017. (invited)

\item A.S. Voyles, \enquote{\href{https://intds2024.ornl.gov/}{Methods for Preparation and Characterization of Thin Arsenic Targets for Stacked Target Experiments (aka:  What Works, and What Doesn’t).}} \nth{31} Conference of the International Nuclear Target Development Society, Knoxville, Tennessee. 20 August 2024.

\item A.S. Voyles, \enquote{Nuclear Data for Isotope Production: Target Fabrication and Reaction Evaluation in the Berkeley Nuclear Data Group.} ORNL Radioisotope Portfolio Seminar, Oak Ridge, Tennessee. 15 August 2024. (invited)

\item A.S. Voyles, \enquote{How the Pølse Gets Made: Target Fabrication for Nuclear and Medical Physics.} Oslo Nuclear Physics Workshop, Oslo, Norway. 14 December 2023. (invited)

\item A.S. Voyles, \enquote{TR-4: Isotope Production Capabilities at Berkeley.} Norwegian Nuclear Research Centre Kickoff Meeting, Oslo, Norway. 11 December 2023. (invited)

\item A.S. Voyles, \enquote{\href{https://indico.bnl.gov/event/18701/}{Review of the LBNL Measurement Program.}} CSEWG Annual Meeting, Upton, New York. 17 November 2023. (invited)


\item A.S. Voyles, \enquote{\href{https://nds.iaea.org/publications/indc/indc-nds-0884/}{Nuclear Data Needs for High-Energy (p,x) Isotope Production \& Evaluation.}} IAEA Technical Meeting on Nuclear Data for Medical Applications, Vienna, Austria. 28 August 2023. (invited)

\item A.S. Voyles, \enquote{\href{https://acs.digitellinc.com/sessions/583121/view}{Methods for preparation and characterization of thin arsenic targets for stacked-target experiments.}} American Chemical Society Fall 2023 Meeting, San Francisco, CA. 17 August 2023. 

\item A.S. Voyles, \enquote{\href{https://conferences.lbl.gov/event/1243/contributions/7407/}{\ce{^{169}Yb} Gamma Calibration Source Production.}} Microcalorimetry and Nuclear Data (MiND 2023), Washington, D.C.. 28 June 2023. (invited)

\item A.S. Voyles, \enquote{\href{https://conferences.lbl.gov/event/1243/contributions/7398/}{Nuclear Data Needs for Auger
Electrons.}} Microcalorimetry and Nuclear Data (MiND 2023), Washington, D.C.. 27 June 2023. (invited)

\item A.S. Voyles, \enquote{\href{https://indico.cern.ch/event/1132769/contributions/5395295/}{Investigating high-energy proton-induced reactions: Implications for level densities and the preequilibrium exciton model.}} \nth{16} Varenna Conference on Nuclear Reaction Mechanisms, Varenna, Italy. 13 June 2023. 

\item A.S. Voyles, \enquote{\href{https://inpp.ohio.edu/~inpp/seminars/abstracts_fall2022/INPP_18Oct22.pdf}{Investigating high-energy proton-induced reactions: Implications for level densities and the preequilibrium exciton model.}} Ohio University Institute of Nuclear \& Particle Physics Seminar Series, Athens, OH. 18 October 2022. (invited)

\item A.S. Voyles, \enquote{Isotope Production Needs for Uncertainty Quantification.} Nuclear Data Uncertainty Quantification Working Meeting, \emph{online}. 12 October 2022. (invited)

\item A.S. Voyles, \enquote{\href{https://meetings.triumf.ca/event/108/contributions/3718/}{Isotope Production Activities at LBNL: The Tri-Lab Effort in Nuclear Data (TREND), and Novel Production Pathways for \ce{^{225}Ac}}.} \nth{18} International Workshop on Targetry and Target Chemistry, Whistler, Canada. 24 August 2022.

\item A.S. Voyles, \enquote{\href{https://www.mn.uio.no/fysikk/english/research/news-and-events/events/conferences/gamma8/program/book_of_abstracts.pdf}{Investigating High-Energy Proton-Induced Reactions: Implications for Level Densities and the Preequilibrium Exciton Model}.}  \nth{8} Workshop on Nuclear Level Density and Gamma Strength, Oslo, Norway. 10 May 2022.

\item A.S. Voyles, \enquote{\href{https://conferences.lbl.gov/event/541/}{Nuclear data for isotope production: From Level Densities to the Bedside}.} Lawrence Berkeley National Laboratory Nuclear Science Division Staff Meeting, Berkeley, CA. 29 June 2021. (invited)



\item A.S. Voyles, \enquote{\href{https://www.morressier.com/o/event/6022c0c2e8bb0500118660c6/article/609136b66e987178c2dc86ae}{Nuclear data for isotope production}.} Symposium on Radiotherapeutics: From Isotope Production to Targeted
Delivery, American Chemical Society Spring 2021 Meeting, \emph{online}. 06 April 2021. (invited)

\item A.S. Voyles, \enquote{\href{https://conferences.lbl.gov/event/504/}{\ce{^{238}U}(p,xn) and \ce{^{235}U}(d,xn) \ce{^{235-237}Np} Nuclear Reaction Cross Sections Relevant to the Production of \ce{^{236g}Np}}.} Workshop for Applied Nuclear Data Activities, \emph{online}. 03 February 2021.

\item A.S. Voyles, \enquote{\href{https://conferences.lbl.gov/event/504/}{Nuclear Data 101: Predictive Codes for Isotope Production}.} Workshop for Applied Nuclear Data Activities, \emph{online}. 27 January 2021. (invited)

\item A.S. Voyles, \enquote{\href{https://conferences.lbl.gov/event/292/}{Targetry Fabrication for Nuclear Data Measurements}.} Workshop for Applied Nuclear Data Activities, Washington, D.C.. 04 March 2020. (invited)

\item A.S. Voyles, \enquote{\href{https://eastbay.nerdnite.com/nerd-nite-624-apollo-11-recovery-oakland-art-deco-radiopharmaceuticals/}{Using New Radiopharmaceuticals to Treat Disease}.} Nerd Nite East Bay, Oakland, CA. 24 June 2019. (invited)

\item A.S. Voyles, \enquote{\href{https://conferences.lbl.gov/event/188/}{Novel Production Methods for \ce{^{225}Ac}}.} Lawrence Berkeley National Laboratory Nuclear Science Division Staff Meeting, Berkeley, CA. 05 March 2019. (invited)

\item A.S. Voyles, \enquote{\href{https://conferences.lbl.gov/event/198/}{Capabilities for Isotope Production Nuclear Data Measurements at LBNL}.} Workshop for Applied Nuclear Data Activities, Washington, D.C.. 23 January 2019. (invited)

\item A.S. Voyles, \enquote{\href{https://lansce.lanl.gov/lug2018.php}{Isotope Production Activities at LANSCE-IPF: Development of a new Nb(p,x)\ce{^{90}Mo} Monitor Reaction and La(p,x) Production Cross-Section Measurements}.} 2018 LANSCE User Group Meeting, Santa Fe, NM. 05 November 2018. (invited)

\item A.S. Voyles, \enquote{\href{https://slideslive.com/38910297/isotope-production-activities-at-lbnl-and-lansceipf-development-of-a-new-nbpx90mo-monitor-reaction-and-felapx-production-crosssection-measurements}{Isotope Production Activities at LBNL and LANSCE-IPF: Development of a new Nb(p,x)\ce{^{90}Mo} Monitor Reaction and Fe,La(p,x) Production Cross-Section Measurements}.} \nth{17} International Workshop on Targetry and Target Chemistry, Coimbra, Portugal. 30 August 2018.


\item A.S. Voyles, \enquote{\href{https://indico.cern.ch/event/686407/contributions/2943775/}{Isotope production cross section measurements at the HFNG, LANL-IPF, and LBNL}.}  \nth{14}  Nordic Meeting on Nuclear Physics, Longyearbyen, Norway. 24 May 2018.

\item A.S. Voyles, \enquote{\href{https://github.com/avoyles/presentations/blob/master/2018-02-12-UCBNE_colloquium/Voyles_12_Feb_2018_NE_Colloquium_Talk.pdf}{Cross-Section Measurements for Novel Medical Radionuclides at UCB/LBNL: The Challenge of \enquote{Simple} Experiments}.} UC Berkeley NE Dept.\ Graduate Colloquium, Berkeley, CA. 12 February 2018. (invited)

\item A.S. Voyles, \enquote{\href{https://github.com/avoyles/presentations/blob/master/2017-05-19-oslo_summer_school/Voyles_19_May_2017_Oslo_Summer_School.pdf}{Medical Isotope Production at Berkeley}.} University of Oslo Nuclear Physics Summer School, Oslo, Norway.  19 May 2017. (invited)

\item A.S. Voyles, \enquote{\href{http://tid.uio.no/workshop2017/talks/OsloWS17_Voyles.pdf}{Spin Distribution of Excited Nuclear States in $^{\text{nat}}$Fe(p,$\alpha$n)}.} \nth{6} Workshop on Nuclear Level Density and Gamma Strength, Oslo, Norway. 08 May 2017.


\item A.S. Voyles, \enquote{\href{https://indico.bnl.gov/event/1743/contributions/3189/}{Experimental Activities in Berkeley}.} US National Nuclear Data Week  (CSEWG), Upton, NY. 14 November 2016.


\item A.S. Voyles, \enquote{\href{https://slideslive.com/38898186/64cu-and-47scnp-crosssection-measurements-for-medical-radionuclide-production}{\ce{^{64}Cu} and \ce{^{47}Sc} (n,p) Cross-Section Measurements for Medical Radionuclide Production}.} \nth{16} International Workshop on Targetry and Target Chemistry, Santa Fe, NM. 30 August 2016.

\item A.S. Voyles, \enquote{\href{https://github.com/avoyles/posters/blob/master/2016-06-07-UITI/Voyles_UITI2016_Poster_OsloUpdate.pdf}{Neutron Cross-Sections for Radionuclide Production}} (Poster).  University \& Industry Technical Interchange 2016 Review Meeting, Raleigh, NC. 07 June 2016.

\item A.S. Voyles, \enquote{GEANT4 Simulation of Irradiation Facilities and Neutron Sources at University of Utah TRIGA for
Nuclear Forensics and Detection.}  AICHE Annual Meeting, Minneapolis, MN. 19 October 2011.

\item A.S. Voyles, \enquote{GEANT4 Simulation of Irradiation Facilities and Neutron Sources at University of Utah TRIGA for
Nuclear Forensics and Detection.}  \nth{2} National Conference in Advancing Tools and Solutions for
Nuclear Material Detection, Salt Lake City, UT. 02 May 2011.

\item A.S. Voyles, \enquote{GEANT4 Simulation of Irradiation Facilities at University of Utah TRIGA (2011).} 
ANS Student Conference, Atlanta, GA. 15 April 2011.

\end{bibsection}


\section{\sc Organization of conferences and symposia}

\begin{list2}

\item Co-Chair,  Microcalorimetry and Nuclear Data (MiND 2023) Workshop,  27--28 June 2023.

\item Session Chair, \enquote{Department of Energy Isotope Programs}, Workshop for Applied Nuclear Data Activities,  27 February -- 02 March 2023.

\item Session Chair, \enquote{Predictive Codes for Isotope Production}, Workshop for Applied Nuclear Data Activities,  25 January -- 03 February 2021.

\end{list2}
