\begin{rSubsection}{Decay-on-Demand}{\textnormal{DARPA}}{Collaborator, Subaward PI}{FY25--FY26}
\item    Two years at \$2,999,971.
\item The goal of this work is to demonstrate and quantify an increase in production yield of novel daughter product radioisotopes in the decay chain of actinide radioisotopes as well as supporting theoretical analysis of the results to understand the underlying physics.


\end{rSubsection}

\begin{rSubsection}{STARFIRE: Nuclear Irradiation and Assay}{\textnormal{Lawrence Livermore National Security}}{PI}{FY25--FY28}
\item    Three years at \$100,000.
\item As a collaborative member of the \href{https://ife.llnl.gov/starfire-hub}{STARFIRE Hub}, the goal of this work is to perform real-time irradiation of the final-stage optics and other critical optical components for inertial fusion energy at the National Ignition Facility.


\end{rSubsection}

\begin{rSubsection}{Building a Nuclear Data Pipeline for Isotope Production}{\textnormal{Isotope R\&D and Production (DOE Isotope Program)}}{Co-PI}{FY24--FY25}
\item    Two years at \$305,143.
\item The goal of this work is to develop an online isotope production planning tool incorporating research and development of AI/ML-augmented reaction evaluations, to  advance  production techniques, increasing the efficiency of radioisotope production.
\item Collaborative project with LANL, BNL, and TAMU.


\end{rSubsection}

\begin{rSubsection}{Nuclear Data for Microcalorimetry}{\textnormal{NNSA Office of International Nuclear Safeguards (NA-241)}}{Co-PI}{FY25--FY26}
\item    Three years at \$1,471,000/year.
\item The goal of this work is to re-determine key gamma-ray emission probabilities for Pu, Am, and U in the 50-208 keV energy range in order for microcalorimeter gamma spectroscopy to reach uncertainty limits in analysis of safeguards samples.
\item We will design and conduct experimental campaigns using complementary detection methods and advanced sample preparation to measure this data.


\end{rSubsection}

\begin{rSubsection}{Data Evaluation for Nuclear Science (DEANS)}{\textnormal{U.S. Nuclear Data Program}}{Collaborator, Subaward PI}{FY22--FY27}
\item    Five years at \$750,850, serving as UC Berkeley Campus PI.
\item Research group tasked with providing nuclear data to help meet the missions of the Lawrence Berkeley National Laboratory component of the US Nuclear Data Program (LBNL-USNDP). 
% \item Carrying out nuclear data measurements, compilation and evaluation. The work is carried out at both LBNL and UC Berkeley as a part of the Bay Area Nuclear Data Group. 
\item UCB members of the DEANS team work under the leadership of Campus PI Voyles to carry out targeted nuclear
data compilation, evaluation and measurement activities at both LBNL and UC Berkeley as a part of the Bay Area Nuclear Data Group. 
% DEANS staff  utilize research equipment at the LBNL 88-Inch cyclotron.


\end{rSubsection}



\begin{rSubsection}{Optimized Deuteron Target Fabrication for Radionuclide Production}{\textnormal{NorthStar RadioIsotopes, LLC}}{Collaborator}{FY21--FY23}
\item    Three years at \$803,464.
\item The goal of this project is to design a target capable of producing multiple medical radionuclides simultaneously using a combination of fast neutrons from thick target deuteron breakup and deuteron-induced fusion evaporation reactions.

\end{rSubsection}

\begin{rSubsection}{Measurement of charged particle-induced nuclear
reaction cross sections important to the Isotope Program at LBNL, LANL, and BNL}{\textnormal{Isotope R\&D and Production (DOE Isotope Program)}}{Collaborator}{FY19--FY23}
\item    Five years at \$750,000.
\item Our goal is to measure proton-induced reaction cross sections for the accelerator-driven production of radioisotopes for medical and national security applications.

\end{rSubsection}


